Hypertension and microbiome

### 2019-06-03 articletwo.Rmd
Top genera

```{r top generas, eval = FALSE, include = FALSE}
abund.genus <- abundances(pseq.genus, transform = "compositional") %>%
    t %>%
    as.data.frame %>%
    tibble::rownames_to_column("id") %>%
    setNames(tolower(replace.brackets(names(.))))

@@

pcoacorabund <- function(names, pcoa) {
    lapply(c2l(abund.genus.bacteria), function (name) 
                     lapply(c2l(1,2,3), function(index) {
                             model <- lm(abund.genus[,name] ~ pcoa[,index])
                             summary(model)$r.squared
                         }))
}

pcoacor.genus <- pcoacorabund(abund.genus.bacteria, pcoa.vectors)
pcoacor.genus.df <- map_df(pcoacor.genus, ~as.data.frame(.x), .id="id")

pcoacor.genus.df %>%
    arrange(-X3) %>%
    head(10) %>% kable
```

>>>>

Genera with top R2 with PCoA axes

```{r top generas}
abund.genus <- abundances(pseq.genus, transform = "compositional") %>%
    t %>%
    as.data.frame %>%
    tibble::rownames_to_column("id") %>%
    setNames(tolower(replace.brackets(names(.))))

@@

abund.df <- merge(pcoa.vectors %>%
                  select("Axis.1", "Axis.2", "Axis.3") %>%
                  tibble::rownames_to_column("id"),
                  abund.genus %>% select(id, abund.genus.bacteria),
                  by = "id") %>%
    merge(.,  meta(pseq.genus) %>% tibble::rownames_to_column("id"), by = "id")

pcoacorabund <- function(df,
                         genera.names,
                         axis.names = c("Axis.1", "Axis.2", "Axis.3")) {
    lapply(c2l(genera.names), function (taxa) 
        lapply(c2l(axis.names), function(axis) {
            fo <- sprintf("%s ~ %s", axis, taxa)
            model <- lm(as.formula(fo), data = df)
            summary(model)$r.squared
        }))
}

pcoacor.genus <- pcoacorabund(abund.df, genera.names = abund.genus.bacteria)
pcoacor.genus.df <- map_df(pcoacor.genus, ~as.data.frame(.x), .id="id")

pcoacor.genus.df %>%
    arrange(-Axis.3) %>%
    head(20) %>% kable
```
